Verification of a Deterministic Random Bits Generator

### 2015-12-27 paper/paper.tex
avoiding widow/orphan lines
wording on proof process

@@

The current proof goal also contains the abstract syntax tree (AST) of the C code. Represented as nodes in the AST, each statement modifies the proof environment, and each step in the proof (left pane) is an instruction to Coq on how to step through the AST. For simple statements, such as an assignment statement, the proof automation system can figure out how the proof environment will be affected by stepping through the statement. Other statements require the proof to explicitly state how the proof environment will be affected. These statements include the \lstinline{if} statement or different kinds of loops.

>>>>

\widowpenalty500
\clubpenalty500

@@

The current proof goal also contains the abstract syntax tree (AST) of the C code. Each statement in the AST modifies the proof environment, and each step in the proof (left pane) is an instruction to Coq on how to step through the AST. For simple statements, such as an assignment statement, the proof automation system can figure out how the proof environment will be affected by stepping through the statement. Other statements require the proof to explicitly state how the proof environment will be affected. These statements include the \lstinline{if} statement or different kinds of loops.
